Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2022-06-16 Paper/Paper.tex
Updates from Overleaf

\begin{figure}[ht]
    \centering
    \caption{Hospitals Receiving Meaningful Use Stage 1 Subsidy}
    \includegraphics[scale=.6]{Objects/QS-Hospitals-Receiving-Payments-for-MU-and-Adoption.png}
    \caption*{Source: HealthIT.gov}
    \label{fig:meanuse}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Screenshot of EHR System}
    \includegraphics[scale=.4]{Objects/epic-ehr-screenshot.jpg}
    \includegraphics[scale=.115]{Objects/EHRimage2.jpg}
    \label{fig:EPIC}
\end{figure}

@@

\begin{figure}[t]
\centering
    \caption{Treatment Variables Over Time}
    \includegraphics[scale=.45]{Objects/sum_stats_year.pdf}
    \label{fig:treatmentgraph}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Hospital EHR Adoption Over Time}
    \includegraphics[scale=.7]{Objects/hosp_treat.pdf}
    \label{fig:hosp_treat}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Retirement}
    \includegraphics[scale=.65]{Objects/retire_plot.pdf}
    \label{fig:retirefirst}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: 0.003 (0.0008), 0.002 (0.0009), 0.005 (0.002), respectively.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Likelihood of Working in Office}
    \includegraphics[scale=.65]{Objects/officeind_plot.pdf}
    \label{fig:officefirst}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: -0.0004 (0.008), -0.004 (0.008), 0.02 (0.02), respectively.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Fraction of Total Patients Seen in Office}
    \includegraphics[scale=.65]{Objects/officefrac_plot.pdf}
    \label{fig:officesecond}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: -0.0003 (0.004), -0.0007 (0.005), -0.006 (0.018), respectively.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Likelihood of Changing Zip Codes}
    \includegraphics[scale=.65]{Objects/zip_plot.pdf}
    \label{fig:zip}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: 0.045 (0.006), 0.046 (0.007), 0.042 (0.018), respectively.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Patient Count}
    \includegraphics[scale=.65]{Objects/patient_plot.pdf}
    \label{fig:patient}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: 14.1 (4.6), 15.8 (5.4), -0.29 (13.0), respectively.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Patient Count by Group}
    \includegraphics[scale=.47]{Objects/patient_group.pdf}
    \label{fig:patientgroup}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} Plot shows average group time treatment effects for each treatment group.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Claim Count}
    \includegraphics[scale=.65]{Objects/claim_plot.pdf}
    \label{fig:claim}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: 4.04 (33.89), 25.77 (31.26), -161.06 (133.35), respectively.}}
\end{figure}

@@

@@

@@

@@

@@

@@

@@

\section{Tables and Figures}

\begin{figure}[ht]
    \centering
    \caption{Comparison of ATT, Low-Integration Treatment Variable}
    \includegraphics[scale=.57]{Objects/LI_graph.pdf}
    \label{fig:LI}
\end{figure}

\begin{figure}[ht]
    \centering
    \caption{ATT With Anticipation}
    \includegraphics[scale=.57]{Objects/anticipation_graph.pdf}
    \label{fig:anticipation}
\end{figure}

\begin{figure}
    \centering
    \caption{Results: Two Way Fixed Effects}
    \includegraphics[scale=.8]{Objects/twfe_plot.pdf}
    \label{fig:twfe}
\end{figure}

\begin{figure}[ht]
    \centering
    \caption{Other Event Study Estimators}
    \includegraphics[scale=.57]{Objects/estimators_graph.pdf}
    \label{fig:esimators}
\end{figure}

\begin{figure}[ht]
    \centering
    \caption{Limited Sample Years}
    \includegraphics[scale=.5]{Objects/years_graph.pdf}
    \label{fig:years}
\end{figure}

\begin{figure}[ht]
    \centering
    \caption{Physicians without Data Assistants}
    \includegraphics[scale=.57]{Objects/DA_graph.pdf}
    \label{fig:DA}
\end{figure}

\begin{figure}[ht]
    \centering
    \caption{Heterogeneity Analysis}
    \includegraphics[scale=.57]{Objects/heterogeneity _graph.pdf}
    \label{fig:het}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \captionsetup{width=.6\linewidth}
    \caption{Hospitals Receiving Meaningful Use Stage 1 Subsidy}
    \includegraphics[scale=.6]{Objects/QS-Hospitals-Receiving-Payments-for-MU-and-Adoption.png}
    \caption*{Source: HealthIT.gov}
    \label{fig:meanuse}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.4\linewidth}
    \caption{Screenshot of EHR System}
    \includegraphics[scale=.4]{Objects/epic-ehr-screenshot.jpg}
    \includegraphics[scale=.115]{Objects/EHRimage2.jpg}
    \label{fig:EPIC}
\end{figure}

@@

\begin{figure}[t]
\centering
\captionsetup{width=.45\linewidth}
    \caption{Treatment Variables Over Time}
    \includegraphics[scale=.45]{Objects/sum_stats_year.pdf}
    \label{fig:treatmentgraph}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.7\linewidth}
    \caption{Hospital EHR Adoption Over Time}
    \includegraphics[scale=.7]{Objects/hosp_treat.pdf}
    \label{fig:hosp_treat}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.85\linewidth}
    \caption{Effect of EHR Exposure on Retirement}
    \includegraphics[scale=.65]{Objects/retire_plot.pdf}
    \label{fig:retirefirst}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: 0.003 (0.0008), 0.002 (0.0009), 0.005 (0.002), respectively.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.85\linewidth}
    \caption{Effect of EHR Exposure on Likelihood of Working in Office}
    \includegraphics[scale=.65]{Objects/officeind_plot.pdf}
    \label{fig:officefirst}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: -0.0004 (0.008), -0.004 (0.008), 0.02 (0.02), respectively.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.85\linewidth}
    \caption{Effect of EHR Exposure on Fraction of Total Patients Seen in Office}
    \includegraphics[scale=.65]{Objects/officefrac_plot.pdf}
    \label{fig:officesecond}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: -0.0003 (0.004), -0.0007 (0.005), -0.006 (0.018), respectively.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.85\linewidth}
    \caption{Effect of EHR Exposure on Likelihood of Changing Zip Codes}
    \includegraphics[scale=.65]{Objects/zip_plot.pdf}
    \label{fig:zip}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: 0.045 (0.006), 0.046 (0.007), 0.042 (0.018), respectively.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.85\linewidth}
    \caption{Effect of EHR Exposure on Patient Count}
    \includegraphics[scale=.65]{Objects/patient_plot.pdf}
    \label{fig:patient}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: 14.1 (4.6), 15.8 (5.4), -0.29 (13.0), respectively.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.6\linewidth}
    \caption{Effect of EHR Exposure on Patient Count by Group}
    \includegraphics[scale=.47]{Objects/patient_group.pdf}
    \label{fig:patientgroup}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} Plot shows average group time treatment effects for each treatment group.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.85\linewidth}
    \caption{Effect of EHR Exposure on Claim Count}
    \includegraphics[scale=.65]{Objects/claim_plot.pdf}
    \label{fig:claim}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: 4.04 (33.89), 25.77 (31.26), -161.06 (133.35), respectively.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.57\linewidth}
    \caption{Comparison of ATT, Low-Integration Treatment Variable}
    \includegraphics[scale=.57]{Objects/LI_graph.pdf}
    \label{fig:LI}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} Aggregated average treatment effects are shown for each outcome variable, along with 95\% confidence intervals. Low-integration hospitals are defined by hospital management.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.57\linewidth}
    \caption{ATT With Anticipation}
    \includegraphics[scale=.57]{Objects/anticipation_graph.pdf}
    \label{fig:anticipation}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} Aggregated average treatment effects are shown for each outcome variable, along with 95\% confidence intervals.}}
\end{figure}

@@

\begin{figure}
    \centering
    \captionsetup{width=.8\linewidth}
    \caption{Results: Two Way Fixed Effects}
    \includegraphics[scale=.8]{Objects/twfe_plot.pdf}
    \label{fig:twfe}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} Event study plots from two way fixed effects estimation are shown for each outcome variable.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.57\linewidth}
    \caption{Other Event Study Estimators}
    \includegraphics[scale=.57]{Objects/estimators_graph.pdf}
    \label{fig:esimators}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} Results from various methods of estimation are shown, along with 95\% confidence intervals.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.57\linewidth}
    \caption{Limited Sample Years}
    \includegraphics[scale=.57]{Objects/years_graph.pdf}
    \label{fig:years}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} Aggregated average treatment effects and 95\% confidence intervals shown for main specification and a limited sample of years.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.57\linewidth}
    \caption{Physicians without Data Assistants}
    \includegraphics[scale=.57]{Objects/DA_graph.pdf}
    \label{fig:DA}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} Aggregated average treatment effects and 95\% confidence intervals shown for main specification and limited sample of physicians who do not work with data assistants.}}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \captionsetup{width=.65\linewidth}
    \caption{Heterogeneity Analysis}
    \includegraphics[scale=.65]{Objects/heterogeneity _graph.pdf}
    \label{fig:het}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} Aggregated average treatment effects and 95\% confidence intervals shown for main specification and various limited samples of physicians.}}
\end{figure}
